### 2023-04-04 README.Rmd
Modifed calcpopC to suite SA. No EWN
Added curryear to hcrfun inside doprojections.

>>>>

* 2023-04-04 aMSE 0.1.0 Added curryear to hcrfun so all HS functions should now include curryear inthier arguments. Within doprojecitons() it is set to year inside the loop. This was needed to allow the SA HS to use its fleet dynamics model and is not needed in Tasmania, but is required in the argument list.

* 2023-03-31 aMSE 0.0.25 Modified calcpopC througout to allow for SA's harvest strategy and fleet dynamics.
